WDIAS : A Microservices-Based Weather Data Integration and Assimilation System\\

### 2020-02-29 ThePaper.tex
Paper: Finalized

\acrfull{lead} is using the fundamental concept of  dynamic workflow orchestration and data management in a Web services framework \cite{Droegemeier2005Service-OrientedWeather}. To predict and analyze weather models by researchers, it required many resources. Rather than each researcher is running and handling their computer resources to do the weather experiments, \acrshort{lead} provides a pool of resources, then the researchers can use the resources pool to run their experiment in shorter amounts of time in higher scale. It is following the \acrfull{soa} with different service layers, and expose services via a drag and drop interface to create new flow by users to run new forecast workflows. A workflow service inside the \acrshort{lead} schedules and run workflows with promising the full use of underline resources in the system. \acrfull{dias}\cite{Kawasaki2018DataReduction} and \acrfull{madis}\cite{Macdermaid2005ARCHITECTUREP2.39} provide the functionality of integration and sharing weather data. When compared to other systems, \acrshort{dias} and \acrshort{madis} do not have the workflow capabilities. To store data on a large volume of disk space, \acrshort{dias} converts the data using a inbuilt set of \acrshort{api}s and provides the functionality of quality control of the data, and metadata management, and shares the data through a Shared API layer. Also, \acrshort{madis} stores the data by converting into a common data format, and provides role based data access.
As mentioned above, most systems are using monolithic architecture or client service architecture, platform dependent, and not up to date with cloud computing technologies. Thus users do not have much flexibility to decide the best cost-effective way to host it. Since most system are proprietary or closed source, it is difficult to add new requirements and maintain the system.

@@

Each extension is considering as a mathematical function which can take \texttt{p} number of input timeseries variables and output \texttt{n} number of timeseries variables. Other than that, at the time of processing the system can configure to provide bind constant which can provide while configuring an extension. This means it is possible to change the behavior of an existing function by providing different bind constant at the time of creating new triggers for an extension. The system allow to create new triggers and update them at the run time via POST requests.

\begin{lstlisting}[language=Python]
{
    "extensionId": "", // An unique identifier for new extension trigger
    "extension": "Interpolation/Transformation/Validation",
    "function": "", // microservice which handles the function mapping
    "variables": [ // Array of timeseries mapping to variables
        {
            "variableId": "",
            "metadata/metadtaIds": {
            }
        }
    ],
    "inputVariables": [], // Input timeseries
    "outputVariables": [], // Output timeseries
    "trigger": [ // When to trigger the function
        {
            "trigger_type": "OnChange/OnTime",
            "trigger_on": []
        }
    ],
    "options": { // Run time bind contant data for the extension
    }
}
\end{lstlisting}

\dbc{Code examples should be included only if they are novel and essential for discussion. If included, key lines in code need to be explained while referring to line numbers.}

Extension Handler is responsible for triggering the correct Extension with metadata when there is any change on the subscribed extension trigger's \emph{OnChange} timeseries.
Extension Handler is responsible for triggering the correct Extension with metadata at a given time which is provided at the creation on extension trigger with the value of OnTime cronjob string value. To improve the performance of triggering cronjobs at given time schedules, the WDIAS added few optimization mechanisms.

@@

Other than the metadata manipulation API mentioned in \cref{psubse:microservice_architecture}, the \acrshort{wdias} also supports timeseries search queries and Geo queries. As an example it can \emph{query timeseries in an area} This operation uses \texttt{geoWithin} search operator for the simplicity. Other than it can also support query timeseries in an area by parameter, query available timeseries by locations and query locations within an area etc.
\begin{lstlisting}
    POST <HOST_NAME>/query/timeseries
    JSON Body:
    {
        "geoJson": {
            "type": "Polygon",
            "coordinates": [
                [
                    [
                        <longitude>,
                        <latitude>
                    ],
                    ...
                ]
            ]
        }
    }
\end{lstlisting}

@@

\begin{table}[ht]
\centering
\caption{\acrshort{eks} nodes}
\begin{adjustbox}{width=0.45\textwidth}
\footnotesize
\begin{tabular}{|l|c|c|c|c|l|}
\hline
\textbf{Node Label} & \textbf{vCPU} & \textbf{RAM (GB)} & \textbf{Storage (GB)} & \textbf{Quantity} & \textbf{EC2 Name} \\ \hline
core & 16 & 32 & 15 & 1 & c5.4xlarge \\ \hline
grid & 8 & 16 & 25 & 1 & c5.2xlarge \\ \hline
scalar & 8 & 16 & 20 & 1 & c5.2xlarge \\ \hline
test & 4 & 10.5 & 5 & 1 & c5n.xlarge \\ \hline
\end{tabular}
\end{adjustbox}
\label{ptab:aws_eks_nodes}
\end{table}

\dbc{All numerical values in tables must to right aligned.}

@@

\begin{table}[htbp]
\caption{ Throughput and Latency of load testing with 60min data}
\begin{center}
\footnotesize
\begin{adjustbox}{width=0.49\textwidth}
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
\textbf{Label} & \textbf{Samples} & \textbf{Avg$^{\mathrm{a}}$} & \textbf{90\%$^{\mathrm{b}}$} & \textbf{S.D.$^{\mathrm{c}}$} & \textbf{Error \%} & \textbf{RPS} \\ \hline
Insert Timeseries & 71826 & 28 & 31 & 58.74 & 0.00\% & 40.5 \\ \hline
Retrieve Timeseries & 71796 & 8 & 10 & 4.18 & 0.00\% & 40.7 \\ \hline
Insert Grid & 7982 & 23 & 26 & 4.23 & 0.06\% & 4.5 \\ \hline
Retrieve Grid & 7979 & 68 & 75 & 10.11 & 0.00\% & 4.5 \\ \hline
Query: Location & 71804 & 3 & 3 & 1.52 & 0.00\% & 40.5 \\ \hline
\textbf{TOTAL} & 311182 & 127 & 503 & 207.80 & 0.00\% & 175.4 \\ \hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Avg: Average Latency, $^{\mathrm{b}}$S.D.: Standard Deviation, $^{\mathrm{c}}$90\%: 90\% percentile.}
\end{tabular}
\end{adjustbox}
\label{ptab:obs_all_60_min_summary_throughput}
\end{center}
\end{table}

@@

\begin{table}[htbp]
\caption{ Throughput and Latency of load testing with 30min data}
\begin{center}
\begin{adjustbox}{width=0.45\textwidth}
\footnotesize
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
\textbf{Label} & \textbf{Samples} & \textbf{Avg$^{\mathrm{a}}$} & \textbf{90\%$^{\mathrm{b}}$} & \textbf{S.D.$^{\mathrm{c}}$} & \textbf{Error \%} & \textbf{RPS} \\ \hline
Insert Timeseries & 71759 & 29 & 32 & 50.97 & 0.00\% & 40.5 \\ \hline
Retrieve Timeseries & 71730 & 9 & 10 & 6.04 & 0.00\% & 40.6 \\ \hline
Insert Grid & 7972 & 44 & 49 & 8.17 & 0.08\% & 4.5 \\ \hline
Retrieve Grid & 7971 & 81 & 93 & 15.15 & 0.00\% & 4.5 \\ \hline
Query: Location & 71734 & 3 & 3 & 1.90 & 0.00\% & 40.5 \\ \hline
TOTAL & 310878 & 129 & 0 & 207.10 & 0.00\% & 175.3 \\ \hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Avg: Average Latency, $^{\mathrm{b}}$S.D.: Standard Deviation, $^{\mathrm{c}}$90\%: 90\% percentile.}
\end{tabular}
\end{adjustbox}
\label{ptab:obs_all_30_min_summary_throughput}
\end{center}
\end{table}

@@

\begin{table}[htbp]
\caption{ Throughput and Latency of load testing with 15min data}
\begin{center}
\begin{adjustbox}{width=0.45\textwidth}
\footnotesize
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
\textbf{Label} & \textbf{Samples} & \textbf{Avg$^{\mathrm{a}}$} & \textbf{90\%$^{\mathrm{b}}$} & \textbf{S.D.$^{\mathrm{c}}$} & \textbf{Error \%} & \textbf{RPS} \\ \hline
Insert Timeseries & 71775 & 30 & 41 & 51.71 & 0.00\% & 40.5 \\ \hline
Retrieve Timeseries & 71736 & 23 & 32 & 50.18 & 0.00\% & 40.6 \\ \hline
Insert Grid & 7975 & 91 & 112 & 19.58 & 1.42\% & 4.5 \\ \hline
Retrieve Grid & 7972 & 118 & 165 & 56.15 & 0.00\% & 4.5 \\ \hline
Query: Location & 71749 & 3 & 4 & 2.32 & 0.00\% & 40.5 \\ \hline
\textbf{TOTAL} & 310934 & 134 & 503 & 206.40 & 0.04\% & 175.4 \\ \hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Avg: Average Latency, $^{\mathrm{b}}$S.D.: Standard Deviation, $^{\mathrm{c}}$90\%: 90\% percentile.}
\end{tabular}
\end{adjustbox}
\label{ptab:obs_all_15_min_summary_throughput}
\end{center}
\end{table}

@@

\begin{table}[htbp]
\caption{Throughput and Latency of load testing with 15min data while enabled K8s
auto-scaling}
\begin{center}
\begin{adjustbox}{width=0.45\textwidth}
\footnotesize
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
\textbf{Label} & \textbf{Samples} & \textbf{Avg$^{\mathrm{a}}$} & \textbf{90\%$^{\mathrm{b}}$} & \textbf{S.D.$^{\mathrm{c}}$} & \textbf{Error \%} & \textbf{RPS} \\ \hline
Insert Timeseries & 71727 & 34 & 27 & 118.78 & 0.00\% & 40.5 \\ \hline
Retrieve Timeseries & 71693 & 7 & 9 & 18.72 & 0.00\% & 40.5 \\ \hline
Insert Grid & 7968 & 87 & 98 & 14.07 & 0.18\% & 4.5 \\ \hline
Retrieve Grid & 7965 & 89 & 110 & 37.79 & 0.00\% & 4.5 \\ \hline
Query: Location & 71704 & 1 & 2 & 2.05 & 0.00\% & 40.5 \\ \hline
\textbf{TOTAL} & 310734 & 130 & 501 & 212.35 & 0.00\% & 175.3 \\ \hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Avg: Average Latency, $^{\mathrm{b}}$S.D.: Standard Deviation, $^{\mathrm{c}}$90\%: 90\% percentile.}
\end{tabular}
\end{adjustbox}
\label{ptab:obs_all_auto_15_min_summary_throughput}
\end{center}
\end{table}

@@

When looking into the \emph{resource utilization} of \acrshort{wdias}; since it is using the \acrshort{k8s} as the container orchestration system, it allows us to scale up and cool down the system as required based on the workload. This demonstrates the test plan of \cref{ptab:obs_all_15_min_summary_throughput}, and the system gets scale up to the maximum at the peak time. Then cool down to a single pod after finishing the test cases.
Given above \acrshort{wdias} can run from 1 CPU node to nodes with 100 CPUs. As described in the \cref{psubse:microservice_architecture}, it uses many of the concepts of modern microservice architecture to create stateless, failover, redundant microservice to achieve such capabilities.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\graphicspath{ {./images/} }
\input{glossary.tex}
\printbibliography[title={References}]
\dbc{References must be in IEEE standard. Some are not quite formatted for IEEE standard. For e.g., some of the paper and conference titles are in upper case.}

>>>>

\acrfull{lead} is using the fundamental concept of  dynamic workflow orchestration and data management in a Web services framework \cite{Droegemeier2005Service-OrientedWeather}. To predict and analyze weather models by researchers, it required many resources. Rather than each researcher is running and handling their computer resources to do the weather experiments, \acrshort{lead} provides a pool of resources, then the researchers can use the resources pool to run their experiment in shorter amounts of time in higher scale. It is following the \acrfull{soa} with different service layers, and expose services via a drag and drop interface to create new flow by users to run new forecast workflows. A workflow service inside the \acrshort{lead} schedules and run workflows with promising the full use of underline resources in the system. \acrfull{dias}\cite{Kawasaki2018DataReduction} and \acrfull{madis}\cite{Macdermaid2005ArchitectureP2.39} provide the functionality of integration and sharing weather data. When compared to other systems, \acrshort{dias} and \acrshort{madis} do not have the workflow capabilities. To store data on a large volume of disk space, \acrshort{dias} converts the data using a inbuilt set of \acrshort{api}s and provides the functionality of quality control of the data, and metadata management, and shares the data through a Shared API layer. Also, \acrshort{madis} stores the data by converting into a common data format, and provides role based data access.
As mentioned above, most systems are using monolithic architecture or client service architecture, platform dependent, and not up to date with cloud computing technologies. Thus users do not have much flexibility to decide the best cost-effective way to host it. Since most system are proprietary or closed source, it is difficult to add new requirements and maintain the system.

@@

Each extension is considering as a mathematical function which can take \texttt{p} number of input timeseries variables and output \texttt{n} number of timeseries variables. Other than that, at the time of processing the system can configure to provide bind constant which can provide while configuring an extension. This means it is possible to change the behavior of an existing function by providing different bind constant at the time of creating new triggers for an extension. The system allow to create new triggers and update them at the run time via API with the POST request body shown in \cref{pli:extension_triggers}.

\begin{lstlisting}[language=Python, caption=Update Extension Triggers API, label=pli:extension_triggers]
{
    "extensionId": "", //Trigger unique identifier
    "extension": "Interpolation | Transformation | Validation",
    "function": "", //Mapping microservice
    "variables": [ //Timeseries mapping to variables
        {
            "variableId": "",
            "metadata/metadtaIds": {...}
        }
    ],
    "inputVariables": [], //Input timeseries
    "outputVariables": [], //Output timeseries
    "trigger": [ // When to trigger the function
        {
            "trigger_type": "OnChange | OnTime",
            "trigger_on": []
        }
    ],
    "options": { //Run time bind constant data
    }
}
\end{lstlisting}

\dbc{Code examples should be included only if they are novel and essential for discussion. If included, key lines in code need to be explained while referring to line numbers.}
\gkc{Updated.}

We implemented the system with possible to create multiple triggers for an extension such as Transformation can have two trigger to sample 1 minute data into 5 minutes data and 1 minute data into hourly data. Each extension trigger need to have a unique identifier as shown in Line 2. Then we allowed users to define the extension type (Line 3) and the microservice which is responsible of processing it (Line 4). User can map timeseries into variable and use them as \emph{X} input and \emph{Y} outputs in the \cref{pfi:summary_weather_data_preprocessing} (Line 5-12). Then provide when to trigger the extension with providing optional data as mentioned in the extension implementation.

\emph{Extension Handler} is responsible for triggering the correct Extension with metadata when there is any change on the subscribed extension trigger's \emph{OnChange} timeseries.
\emph{Extension Handler} is responsible for triggering the correct Extension with metadata at a given time which is provided at the creation on extension trigger with the value of \emph{OnTime} cronjob string value. To improve the performance of triggering cronjobs at given time schedules, the WDIAS added few optimization mechanisms.

@@

Other than the metadata manipulation API mentioned in \cref{psubse:wdias_microservices}, the \acrshort{wdias} also supports timeseries search queries and Geo queries. As an example it can \emph{query timeseries available in a given area}. This operation uses \texttt{geoWithin} search operator for the simplicity. Other than it can also support query timeseries in an area by parameter, query available timeseries by locations and query locations within an area etc. In \cref{pli:geo_search}, the \acrshort{wdias} return the timeseries available within the area of a polygon provided as \emph{geoJson} \cite{InternetEngineeringTaskForceGeoJSON}.

\begin{lstlisting}[caption=Geo search timeseries, label=pli:geo_search]
    POST <HOST_NAME>/query/timeseries
    JSON Body:
    {
        "geoJson": {
            "type": "Polygon",
            "coordinates": [
                [
                    [<longitude>, <latitude>],
                    ...
                ]
            ]
        }
    }
\end{lstlisting}

@@

\begin{table}[htbp]
\caption{\acrshort{eks} nodes}
\begin{center}
\begin{adjustbox}{width=0.45\textwidth}
\begin{tabular}{|l|r|r|r|r|l|}
\hline
\textbf{Node Label} & \textbf{vCPU} & \textbf{RAM (GB)} & \textbf{Storage (GB)} & \textbf{Quantity} & \textbf{EC2 Name} \\ \hline
core & 16 & 32 & 15 & 1 & c5.4xlarge \\ \hline
grid & 8 & 16 & 25 & 1 & c5.2xlarge \\ \hline
scalar & 8 & 16 & 20 & 1 & c5.2xlarge \\ \hline
test & 4 & 10.5 & 5 & 1 & c5n.xlarge \\ \hline
\end{tabular}
\end{adjustbox}
\label{ptab:aws_eks_nodes}
\end{center}
\end{table}

\dbc{All numerical values in tables must to right aligned.}
\gkc{Updated. Fixed the tables.}

@@

\begin{table}[htbp]
\centering
\caption{Throughput and Latency of load testing with 60min data}
\begin{adjustbox}{width=0.45\textwidth}
% \footnotesize
\begin{tabular}{|l|r|r|r|r|r|r|}
\hline
\textbf{Label} & \textbf{Samples} & \textbf{Avg} & \textbf{90\%$^{\mathrm{a}}$} & \textbf{S.D.$^{\mathrm{b}}$} & \textbf{Error \%} & \textbf{RPS} \\ \hline
Insert Timeseries & 71826 & 28 & 31 & 58.74 & 0.00\% & 40.5 \\ \hline
Retrieve Timeseries & 71796 & 8 & 10 & 4.18 & 0.00\% & 40.7 \\ \hline
Insert Grid & 7982 & 23 & 26 & 4.23 & 0.06\% & 4.5 \\ \hline
Retrieve Grid & 7979 & 68 & 75 & 10.11 & 0.00\% & 4.5 \\ \hline
Query: Location & 71804 & 3 & 3 & 1.52 & 0.00\% & 40.5 \\ \hline
\textbf{TOTAL} & 311182 & 127 & 503 & 207.80 & 0.00\% & 175.4 \\ \hline
\multicolumn{4}{l}{$^{\mathrm{a}}$S.D.: Standard Deviation}{$^{\mathrm{b}}$90\%: 90\% percentile}
\end{tabular}
\end{adjustbox}
\label{ptab:obs_all_60_min_summary_throughput}
\end{table}

@@

\begin{table}[htbp]
\caption{ Throughput and Latency of load testing with 30min data}
\begin{center}
\begin{adjustbox}{width=0.45\textwidth}
% \footnotesize
\begin{tabular}{|l|r|r|r|r|r|r|}
\hline
\textbf{Label} & \textbf{Samples} & \textbf{Avg} & \textbf{90\%$^{\mathrm{a}}$} & \textbf{S.D.$^{\mathrm{b}}$} & \textbf{Error \%} & \textbf{RPS} \\ \hline
Insert Timeseries & 71759 & 29 & 32 & 50.97 & 0.00\% & 40.5 \\ \hline
Retrieve Timeseries & 71730 & 9 & 10 & 6.04 & 0.00\% & 40.6 \\ \hline
Insert Grid & 7972 & 44 & 49 & 8.17 & 0.08\% & 4.5 \\ \hline
Retrieve Grid & 7971 & 81 & 93 & 15.15 & 0.00\% & 4.5 \\ \hline
Query: Location & 71734 & 3 & 3 & 1.90 & 0.00\% & 40.5 \\ \hline
TOTAL & 310878 & 129 & 0 & 207.10 & 0.00\% & 175.3 \\ \hline
\multicolumn{4}{l}{$^{\mathrm{a}}$S.D.: Standard Deviation}{$^{\mathrm{b}}$90\%: 90\% percentile}
\end{tabular}
\end{adjustbox}
\label{ptab:obs_all_30_min_summary_throughput}
\end{center}
\end{table}

@@

\begin{table}[htbp]
\caption{ Throughput and Latency of load testing with 15min data}
\begin{center}
\begin{adjustbox}{width=0.45\textwidth}
% \footnotesize
\begin{tabular}{|l|r|r|r|r|r|r|}
\hline
\textbf{Label} & \textbf{Samples} & \textbf{Avg} & \textbf{90\%$^{\mathrm{a}}$} & \textbf{S.D.$^{\mathrm{b}}$} & \textbf{Error \%} & \textbf{RPS} \\ \hline
Insert Timeseries & 71775 & 30 & 41 & 51.71 & 0.00\% & 40.5 \\ \hline
Retrieve Timeseries & 71736 & 23 & 32 & 50.18 & 0.00\% & 40.6 \\ \hline
Insert Grid & 7975 & 91 & 112 & 19.58 & 1.42\% & 4.5 \\ \hline
Retrieve Grid & 7972 & 118 & 165 & 56.15 & 0.00\% & 4.5 \\ \hline
Query: Location & 71749 & 3 & 4 & 2.32 & 0.00\% & 40.5 \\ \hline
\textbf{TOTAL} & 310934 & 134 & 503 & 206.40 & 0.04\% & 175.4 \\ \hline
\multicolumn{4}{l}{$^{\mathrm{a}}$S.D.: Standard Deviation}{$^{\mathrm{b}}$90\%: 90\% percentile}
\end{tabular}
\end{adjustbox}
\label{ptab:obs_all_15_min_summary_throughput}
\end{center}
\end{table}

@@

\begin{table}[htbp]
\caption{Throughput and Latency of load testing with 15min data while enabled K8s auto-scaling}
\begin{center}
\begin{adjustbox}{width=0.45\textwidth}
\footnotesize
\begin{tabular}{|l|r|r|r|r|r|r|}
\hline
\textbf{Label} & \textbf{Samples} & \textbf{Avg} & \textbf{90\%$^{\mathrm{a}}$} & \textbf{S.D.$^{\mathrm{b}}$} & \textbf{Error \%} & \textbf{RPS} \\ \hline
Insert Timeseries & 71727 & 34 & 27 & 118.78 & 0.00\% & 40.5 \\ \hline
Retrieve Timeseries & 71693 & 7 & 9 & 18.72 & 0.00\% & 40.5 \\ \hline
Insert Grid & 7968 & 87 & 98 & 14.07 & 0.18\% & 4.5 \\ \hline
Retrieve Grid & 7965 & 89 & 110 & 37.79 & 0.00\% & 4.5 \\ \hline
Query: Location & 71704 & 1 & 2 & 2.05 & 0.00\% & 40.5 \\ \hline
\textbf{TOTAL} & 310734 & 130 & 501 & 212.35 & 0.00\% & 175.3 \\ \hline
\multicolumn{4}{l}{$^{\mathrm{a}}$S.D.: Standard Deviation}{$^{\mathrm{b}}$90\%: 90\% percentile}
\end{tabular}
\end{adjustbox}
\label{ptab:obs_all_auto_15_min_summary_throughput}
\end{center}
\end{table}

@@

When looking into the \emph{resource utilization} of \acrshort{wdias}; since it is using the \acrshort{k8s} as the container orchestration system, it allows us to scale up and cool down the system as required based on the workload. This demonstrates the test plan of \cref{ptab:obs_all_15_min_summary_throughput}, and the system gets scale up to the maximum at the peak time. Then cool down to a single pod after finishing the test cases.
Given above \acrshort{wdias} can run from 1 CPU node to nodes with 100 CPUs. As described in the \cref{pse:wdias_architecture}, it uses many of the concepts of modern microservice architecture to create stateless, failover, redundant microservice to achieve such capabilities.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\graphicspath{ {./images/} }
\input{glossary.tex}
\printbibliography[title={References}]
\dbc{References must be in IEEE standard. Some are not quite formatted for IEEE standard. For e.g., some of the paper and conference titles are in upper case.}
\gkc{I got your point. But I used this IEEE template: https://www.overleaf.com/latex/templates/ieee-conference-template-example/nsncsyjfmpxy. Not sure how to fix it. May be need to edit the Class implementation above.}
\gkc{Updated. Mendeley has imported them in Upper case. Still is there any issue?}
